Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-22 chapters/introduction/introduction.tex
background for cross-view imagery

\subsection{Overhead Imagery}
Overhead imagery plays an import role in the cross-view learning area.
To construct a cross view image pair, we need to know the geographic
location (sometimes also with the geographic orientation).
\todo{rewrite the following} Efforts have been made to
automate overhead image analysis. As early as
1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.

Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
download the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.

>>>>

\subsection{Cross-view Imagery}
Since the cross-view imagery plays an important role in geolocalization,
we spare an seperate section to introduce it. The cross-view image
pair consists of a ground-view image and an overhead imager at the
same location. In some cases, the ground/overhead images are also
aligned in orientation.
Specifically, Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches extract the features of it as reference
database~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}

Furthermore, there are many other properties of the cross-view pairs
to explore for high-level feature extraction \todo{expand}.
